### 2014-04-07 text/Chapter01.tex
Early work on chapter 3
Finish section 3.1 on coeffect structures

\subsection{Context-awareness \#4: Checking array access patterns}

@@

\subsection{Context-aware language in action}

@@

\section{Theory of context dependence}

@@

\paragraph{Type systems.}
A type system is a form of static analysis that is usually specified by \emph{typing judgements}
such as $\Gamma \vdash e : \tau$. The judgement specifies that, given some variables described by
the context $\Gamma$, the expression $e$ has a type $\tau$. 
The variable context $\Gamma$ is necessary to determine the type of expressions. Consider an 
expression $x + y$. In many languages, including Java, C\# and F\#, the type could be \ident{int}
or \ident{float}, depending on the types of the variables. For example, the following is a valid
typing judgement in F\#:
%
\begin{equation*}
x\-:\-\ident{int},~y\-:\-\ident{int} \vdash x+y : \ident{int}
\end{equation*}
%
This judgement assumes that the type of both $x$ and $y$ is \ident{int} and so the result must also
be \ident{int}. The expression would also be typeable in a context $x\-:\-\ident{int},~y\-:\-\ident{int}$,
but not, for example, in a context where $x$ has a type \ident{unit}.

\paragraph{Tracking evaluation effects.}
Type systems can be extended in numerous ways. The types can be more precise, for example, by specifying
the range of an integer. However, it is also possible to track what program \emph{does} when executed.
In ML-like languages, the following is a valid judgement:
%
\begin{equation*}
x\-:\-\ident{int} \vdash \ident{print}~x : \ident{unit}
\end{equation*}
%
The judgement states that the expression $\ident{print}~x$ has a type \ident{unit}. This is correct, 
but it ignores the important fact that the expression has a \emph{side-effect} and prints a number
to the console. In purely functional languages, this would not be possible. For example, in Haskell,
the type would be $\ident{IO unit}$ meaning that the result is a \emph{computation} that performs I/O
effects and then returns \ident{unit} value.

Another option for tracking effects is to extend the judgement with additional information 
about the effects. The judgement in a language with effect system would look as follows:
%
\begin{equation*}
x\-:\-\ident{int} \vdash \ident{print}~x : \ident{unit~\&~\{ console \}}
\end{equation*}
%
Effect systems add \emph{effect annotation} as another component of the typing judgement. In the above
example, the return type is \ident{unit}, but the effect annotation informs us that the expression
also accesses \ident{console} as part of the evaluation. To track such information, the compiler needs
to understand the effects of primitive built-in functions -- such as \ident{print}.

@@

The systems for tracking of context requirements developed in this thesis are inspired by the idea
of effect systems. To demonstrate our approach, consider the following call from the sample program
shown earlier -- first using standard ML-like type system:
%
\begin{equation*}
\ident{password}\-:\-\ident{string},~\ident{cmd}\-:\-\ident{string} 
  \vdash \ident{query}(\ident{cmd}, \ident{password}) : \ident{news list}
\end{equation*}
%
The expression queries a database and gets back a list of news values as the result. Recall from the
earlier discussion that there are two contextual information that are desirable to track for this 
expression. First, the call to the \ident{query} primitive requires \emph{database access}. Second,
the \ident{password} argument needs to be marked as \emph{sensitive value} to avoid sending it over
an unsecure network connection.
The \emph{coeffect systems} developed in this thesis capture this information in the following way: 
%
\begin{equation*}
\begin{array}{l}
 ( \ident{password}\-:\-\ident{string \hspace{-1em}{\footnotesize @ sensitive}},
   \ident{cmd}\-:\-\ident{string})
 \hspace{-0.5em}
 \ident{\footnotesize @ \{ database \}} \vdash \\[-0.1em]
 \hspace{3em} \ident{query}(\ident{cmd}, \ident{password}) : \ident{news list}
\end{array}
\end{equation*}
%
Rather than attaching the annotation to the \emph{resulting type}, we attach them to the variable
context $\Gamma$. In other words, coeffect systems track more detailed information about the context,
not just the available variables. In the above example, it tracks meta-data about the variables
and annotates \ident{password} as sensitive. Furthermore, it tracks requirements about the execution
environment -- for example, that the execution requires an access to database.

>>>>

\subsection{Context-awareness \#4: Checking array access patterns}
\label{sec:intro-why-array}

@@

\subsection{Context-aware language in action}
\label{sec:intro-context-example}

@@

\section{Theory of context dependence}
\label{sec:intro-theory}

@@

\paragraph{Type systems.}
A type system is a form of static analysis that is usually specified by \emph{typing judgements}
such as $\Gamma \vdash e : \tau$. The judgement specifies that, given some variables described by
the context $\Gamma$, the expression $e$ has a type $\tau$. 
The variable context $\Gamma$ is necessary to determine the type of expressions. Consider an 
expression $x + y$. In many languages, including Java, C\# and F\#, the type could be \ident{int}
or \ident{float}, depending on the types of the variables. For example, the following is a valid
typing judgement in F\#:
%
\begin{equation*}
x\!:\!\ident{int},~y\!:\!\ident{int} \vdash x+y : \ident{int}
\end{equation*}
%
This judgement assumes that the type of both $x$ and $y$ is \ident{int} and so the result must also
be \ident{int}. The expression would also be typeable in a context $x\!:\!\ident{int},~y\!:\!\ident{int}$,
but not, for example, in a context where $x$ has a type \ident{unit}.

\paragraph{Tracking evaluation effects.}
Type systems can be extended in numerous ways. The types can be more precise, for example, by specifying
the range of an integer. However, it is also possible to track what program \emph{does} when executed.
In ML-like languages, the following is a valid judgement:
%
\begin{equation*}
x\!:\!\ident{int} \vdash \ident{print}~x : \ident{unit}
\end{equation*}
%
The judgement states that the expression $\ident{print}~x$ has a type \ident{unit}. This is correct, 
but it ignores the important fact that the expression has a \emph{side-effect} and prints a number
to the console. In purely functional languages, this would not be possible. For example, in Haskell,
the type would be $\ident{IO unit}$ meaning that the result is a \emph{computation} that performs I/O
effects and then returns \ident{unit} value.

Another option for tracking effects is to extend the judgement with additional information 
about the effects. The judgement in a language with effect system would look as follows:
%
\begin{equation*}
x\!:\!\ident{int} \vdash \ident{print}~x : \ident{unit~\&\aclrd{\{ console \}}}
\end{equation*}
%
Effect systems add \emph{effect annotation} as another component of the typing judgement. In the above
example, the return type is \ident{unit}, but the effect annotation informs us that the expression
also accesses \ident{console} as part of the evaluation. To track such information, the compiler needs
to understand the effects of primitive built-in functions -- such as \ident{print}.

@@

The systems for tracking of context requirements developed in this thesis are inspired by the idea
of effect systems. To demonstrate our approach, consider the following call from the sample program
shown earlier -- first using standard ML-like type system:
%
\begin{equation*}
\ident{password}\!:\!\ident{string},~\ident{cmd}\!:\!\ident{string} 
  \vdash \ident{query}(\ident{cmd}, \ident{password}) : \ident{news list}
\end{equation*}
%
The expression queries a database and gets back a list of news values as the result. Recall from the
earlier discussion that there are two contextual information that are desirable to track for this 
expression. First, the call to the \ident{query} primitive requires \emph{database access}. Second,
the \ident{password} argument needs to be marked as \emph{sensitive value} to avoid sending it over
an unsecure network connection.
The \emph{coeffect systems} developed in this thesis capture this information in the following way: 
%
\begin{equation*}
\begin{array}{l}
 ( \ident{password}\!:\!\ident{string \hspace{-1em}{\footnotesize @ \aclrd{sensitive}}},
   \ident{cmd}\!:\!\ident{string})
 \hspace{-0.5em}
 \ident{\footnotesize @ \aclrd{\{ database \}}} \vdash \\[-0.1em]
 \hspace{3em} \ident{query}(\ident{cmd}, \ident{password}) : \ident{news list}
\end{array}
\end{equation*}
%
Rather than attaching the annotation to the \emph{resulting type}, we attach them to the variable
context $\Gamma$. In other words, coeffect systems track more detailed information about the context,
not just the available variables. In the above example, it tracks meta-data about the variables
and annotates \ident{password} as sensitive. Furthermore, it tracks requirements about the execution
environment -- for example, that the execution requires an access to database.

### 2014-04-07 text/Chapter03.tex
Finish section 3.1 on coeffect structures

\begin{figure}
\[
\tyrule{abs-pure}
  { \Gamma, x\-:\-\tau_1 \vdash e : \tau_2}
  { \Gamma \vdash \lambda x.e : \tau_1 \rightarrow \tau_2 1}
\;\;
\tyrule{abs-eff}
  { \Gamma, x\-:\-\tau_1 \vdash e : \tau_2 \,\&\, \aclrd{\sigma} }
  { \Gamma \vdash \lambda x.e : \tau_1 \xrightarrow{\aclrd{\sigma}} \tau_2 \,\&\, \aclrd{\emptyset} }
\]
\caption{Lambda abstraction for pure and effectful computations}
\label{fig:applications-abs}
\end{figure}

@@

In Chapter~\ref{ch:intro}, we used \emph{resources} in a distributed system as an example of flat
coeffects. These could be, for example, a database, GPS sensor or access to current time.
We also outlined that such context requirements can be tracked as part of the typing assumption,
for example, say we have an expression $e$ that requires GPS and current time. The context of
such expression will be $\coctx{\Gamma}{ \aclrd{\ident{\{ gps, time \}}} }$.

@@

In the example discussed here, $\lambda x.e$ would require a context 
$\coctx{\Gamma}{ \aclrd{\ident{\{ gps \}}} }$

Context requirements in distributed systems can be satisfied in a number of ways. When the 
resource is available locally,

In distributed 
systems, additional resources available at certain nodes (\eg~a database or GPS sensor) can be 
also viewed as a part of typing assumptions.

Similarly, resources in a distributed system can be satisfied by both the declaration site (by 
capturing a remote reference) and the call site (by resource rebinding)~\cite{app-distributed-acute}. 
In this case, the resource requirements are split freely.

We discuss this example in detail in Section~X.

@@

The previously described notion of a \emph{coeffect system} \cite{petricek2013coeffects} tracks
contextual properties of entire programs, which is practically useful for implicit parameters 
or resources. However, for per-variable coeffects, the previous work provides only an approximation 
with limited practical usefulness (\eg~marking the whole context as live when just one 
variable in the context is live).

Furthermore, contextual requirements may relate to 
specific variables. For example, liveness or access patterns, such as the number of accesses in 
bounded linear logic or past values in causal dataflow.

For contextual properties associated with 
variables (\eg~liveness or dataflow), the splitting tracks free variables -- requirements associated 
with a \emph{bound} variable should be satisfied by the call site, while those associated with 
\emph{free} variables should be provided by the declaration site.

lambda abstraction places 
requirements on both the \emph{call-site} (latent requirements) and the \emph{declaration-site} 
(immediate requirements),

 We start with some background and finish with a brief overview of the literature leading to coeffects.

In the rest of the chapter, we look at instances of both. But before, we need to look at vectors.

@@

The $\lambda$-calculus is asymmetric-- it maps a context with \emph{multiple} variables to a 
\emph{single} result. An expression with $n$ free variables of types $\sigma_i$ can be modelled
by a function
$\sigma_1 \times \ldots \times \sigma_n \rightarrow \tau$ with a product on the left, but a single value
on the right. Effect systems attach effect annotations to the result $\tau$. In coeffect systems,
we attach coeffects to the context $\sigma_1 \times \ldots \times \sigma_n$ and we often (but not always)
have one coeffect per each variable. We call the overall coeffect a \emph{vector} consisting of
\emph{scalar} coeffects. This asymmetry explains why coeffect systems are not trivially dual to 
effect systems.

It is useful to clarify how vectors are used in this paper. Suppose we have a set $\C$ of
\emph{scalars} such as $\cclrd{r_1},\ldots,\cclrd{r_n} \in \C$. A vector $\aclrd{R}$ over $\C$
is a tuple $\langle \cclrd{r_1}, \ldots, \cclrd{r_n}\rangle$ of scalars. 
We use letters like $\aclrd{R}, \aclrd{S}, \aclrd{T}$ for 
vectors and $\cclrd{r},\cclrd{s},\cclrd{t}$ for scalars.\footnote{For better readability, the paper 
distinguishes different structures using colours. However ignoring the colour does not introduce 
any ambiguity.} We also say that a \emph{shape} of a vector $\slift{\aclrd{R}}$ (or more generally any container) 
is the set of \emph{positions} in a vector. So, a vector of length
$n$ has shape $\{ 1, 2, \ldots, n \}$.

Just as in scalar-vector multiplication, we lift any binary operation on scalars into a scalar-vector one:
$\cclrd{s} \bullet \aclrd{R} = \langle \cclrd{s}\bullet\cclrd{r_1}, \ldots, \cclrd{s}\bullet\cclrd{r_n}\rangle$.
Given two vectors $\aclrd{R},\aclrd{S}$ of the same shape, containing partially ordered scalars, we 
write $\aclrd{R} \leq \aclrd{S}$ for the pointwise extension of $\leq$ on scalars. Finally,
the associative operation $\times$ concatenates vectors.

@@

\paragraph{Implicit parameters} In Haskell, implicit parameters \cite{app-implicit-parameters} are 
a special kind of variables that may behave as dynamically scoped. This means, if a function uses 
parameter $\ident{?p}$, then the caller of the function must define $\ident{?p}$ and set its value.
Implicit parameters can be used to parameterise a computation (involving a chain of function calls)
without passing parameters explicitly as additional arguments of all involved functions. A simple 
language with implicit parameters has an expression $\ident{?p}$ to read a parameter value and an 
expression\footnote{Haskell uses $\kvd{let}~\ident{?p} = e_1~\kvd{in}~e_2$, but we use a different keyword to 
avoid confusion.} $\kvd{letdyn}~?p = e_1~\kvd{in}~e_2$ that sets a parameter $\ident{?p}$ to the value of $e_1$ 
and evaluates $e_2$ in a context containing $\ident{?p}$

@@

\paragraph{Type classes}
Implicit parameters are closely related to \emph{type classes} \cite{app-type-classes}. In Haskell,
type classes provide a principled form of ad-hoc polymorphism (overloading). When a code uses 
an overloaded operation (e.g.~comparison or numeric operators) a constraint is placed on the 
context in which the operation is used. For example:
%
\begin{equation*}
\begin{array}{l}
\ident{twoTimes}~::~\ident{Num}~\alpha \Rightarrow \alpha \rightarrow \alpha \\
\ident{twoTimes}~x=x+x
\end{array}
\end{equation*}
%
The constraint $\ident{Num}~a$ on the function type arises from the use of the $+$ operator. 
From the implementation perspective, the type class constraint means that the function takes 
a hidden parameter -- a dictionary that provides the operation $+ :: \alpha \rightarrow \alpha \rightarrow \alpha$.
Thus, the type $\ident{Num}~\alpha \Rightarrow \alpha \rightarrow \alpha$ can be viewed as
$(\ident{Num}_\alpha \times \alpha) \rightarrow \alpha$. Implicit parameters work in exactly
the same way -- they are passed around as hidden parameters.

@@

\paragraph{Rebindable resources}
The need for parameters that do not strictly follow static scoping rules also arises in distributed
computing. This problem has been addressed, for example, by Bierman et al. and Sewell et al. 
\cite{app-distributed-rebinding,app-distributed-acute}. To quote the first work: \emph{``Dynamic 
binding is required in various guises, for example when a marshalled value is received from the 
network, containing identifiers that must be rebound to local resources.''}

>>>>

\begin{figure}
\[
\tyrule{abs-pure}
  { \Gamma, x\!:\!\tau_1 \vdash e : \tau_2}
  { \Gamma \vdash \lambda x.e : \tau_1 \rightarrow \tau_2 1}
\;\;
\tyrule{abs-eff}
  { \Gamma, x\!:\!\tau_1 \vdash e : \tau_2 \,\&\, \aclrd{\sigma} }
  { \Gamma \vdash \lambda x.e : \tau_1 \xrightarrow{\aclrd{\sigma}} \tau_2 \,\&\, \aclrd{\emptyset} }
\]
\caption{Lambda abstraction for pure and effectful computations}
\label{fig:applications-abs}
\end{figure}

@@

In Section~\ref{sec:intro-context-example}, we used \emph{resources} in a distributed system as an 
example of flat coeffects. These could be, for example, a database, GPS sensor or access to the current 
time. We also outlined that such context requirements can be tracked as part of the typing assumption,
for example, say we have an expression $e$ that requires GPS coordinates and the current time. 
The context of such expression will be $\coctx{\Gamma}{ \aclrd{\ident{\{ gps, time \}}} }$.

@@

In the example discussed here, $\lambda x.e$ would require GPS sensor from the declaration
site (lexical scope) where the function is declared, which is attached to the current context
as $\coctx{\Gamma}{ \aclrd{\ident{\{ gps \}}} }$. The current time is required from the caller
of the function. So, the context requirement on the call site (dynamic scope) will be
$\aclrd{r}=\aclrd{\footnotesize\ident{\{ time \}}}$. In coeffect systems, we attach this information
to the function writing $\tau_1 \xrightarrow{ \aclrd{r} } \tau_2$.

We look at resources in distributed programming in more details in Section~\ref{sec:applications-flat-distr}.
The important point here is that in flat coeffect systems, contextual requirements are 
\emph{split} between the call-site and declaration-site. Furthermore, in case of distributed
programming, the resources can be freely distributed between the two sites.

@@

On the one hand, variable context provides a \emph{fine-grained tracking} mechanism of how context
(variables) are used. On the other hand, flat coeffects let us track \emph{additional information} about 
the context. The purpose of \emph{structural coeffects} is to reconcile the two and to provide a way
for fine-grained tracking of additional information related to variables in programs.

In Section~\ref{sec:intro-why-array}, we used an example of tracking array access patterns. For every
variable, the additional coeffect annotation keeps a range of indices that may be accessed relatively
to the current cursor. For example, consider an expression 
$x[\kvd{cursor}] = y[\kvd{cursor}-1] + y[\kvd{cursor}+1]$.

Here, the variable context $\Gamma$ contains two variables, both of type \ident{Arr}. This means
$\Gamma = x\!:\!\ident{Arr},\, y\-!\-!\ident{Arr}$. For simplicity, we treat \kvd{cursor} as a 
language primitive. The coeffect annotations will be $(0,0)$ for $x$ and $(-1,1)$ for $y$, 
denoting that we access only the current value in $x$, but we need access to both left and right 
neighbours in the $y$ array. In order to unify the flat and structural notions, we attach this information 
as a \emph{vector} of annotations associated with a \emph{vector} of variable and write:
$\coctx{x\!:\!\ident{Arr},\, y\!:\!\ident{Arr}}{ \aclrd{\alift{ (0,0), (-1,1) }} }$.
The unification is discussed in Chapter~\ref{ch:unified}.

Unlike in flat coeffects, in the structural systems, splitting of context determined by the syntax. 
For example, consider a function that takes $y$ and contains the above body:
$\lambda y.x[\kvd{cursor}] = y[\kvd{cursor}-1] + y[\kvd{cursor}+1]$. Here, the declaration site
contains $x$ and needs to provide access at least within a range $(0,0)$. The call site provides
a value for $y$, which needs to be accessible at least within $(-1, 1)$. In this way, structural
coeffects remove the non-determinism of flat coeffect systems.

Before looking at concrete flat and structural systems in mode details, we briefly overview 
some notation used in this thesis. As structural coeffects keep annotations as \emph{vectors},
we use a number of operations related to scalars and vectors.

@@

The $\lambda$-calculus is asymmetric -- it maps a context with \emph{multiple} variables to a 
\emph{single} result. An expression with free variables of types $\tau_i$ can be modelled by a function 
$\tau_1 \times \ldots \times \tau_n \rightarrow \tau$ with a product on the left, but a single value
on the right. Effect systems attach effect annotations to the result $\tau$. In coeffect systems,
we attach a coeffect annotation to the context $\tau_1 \times \ldots \times \tau_n$.

Structural coeffects have one coeffect annotation per each variable. Thus, the annotation consists
of multiple values -- one belonging to each variable. To distinguish between the overall annotation
and individual (per-variable) annotations, we call the overall coeffect a \emph{vector} consisting of 
\emph{scalar} coeffects. This asymmetry also explains why coeffect systems are not trivially dual to 
effect systems.

It is useful to clarify how vectors are used in this thesis. Suppose we have a set $\C$ of
\emph{scalars} such that $\cclrd{r_1},\ldots,\cclrd{r_n} \in \C$. A vector $\aclrd{R}$ 
over $\C$ is a tuple $\alift{ \cclrd{r_1}, \ldots, \cclrd{r_n} }$ of scalars. 
We use upper-case letters like $\aclrd{R}, \aclrd{S}, \aclrd{T}$ for vectors and lower-case
letters $\cclrd{r},\cclrd{s},\cclrd{t}$ for scalars\footnote{For better readability, the thesis
also distinguishes different structures using colours. However ignoring the colour does not introduce 
any ambiguity.}. We also say that a \emph{shape} of a vector $\slift{\aclrd{R}}$ (or more generally any container) 
is the set of \emph{positions} in a vector. So, a vector of length $n$ has shape $\{ 1, 2, \ldots, n \}$. 
We discuss containers and shapes further in Chapter~\ref{ch:unified} and also discuss how our use
relates to containers of Abbott, Altenkirch and Ghani \cite{types-containers}.

Just as in the usual multiplication of a vector by scalar, we lift any binary operation on scalars into a 
scalar-vector one. For any binary operation on scalars $\circ : \C \times \C \rightarrow \C$, we define
 $\cclrd{s} \circ \aclrd{R} = \alift{ \cclrd{s}\circ\cclrd{r_1}, \ldots, \cclrd{s}\circ\cclrd{r_n}}$.
Relations on scalars can be also lifted to vectors. Given two vectors $\aclrd{R}, \aclrd{S}$ of the
same shape with positions $\{ 1, \ldots, n \}$ and a relation $\varpropto\, \subseteq \C \times \C$ we define 
$\aclrd{R} \varpropto \aclrd{S} \Leftrightarrow (\cclrd{r_1} \varpropto \cclrd{s_1}) \wedge \ldots \wedge (\cclrd{r_n} \varpropto \cclrd{s_n}) $
Finally, we often concatenate vectors -- for example, when joining two variable contexts.
Given vectors $\aclrd{R}, \aclrd{S}$ with (possibly different) shapes $\{ 1, \ldots, n \}$ and 
$\{ 1, \ldots, m \}$, the associative operation for concatenation $\times$ is defined as 
$\aclrd{R}\times\aclrd{S} = \alift{\cclrd{r_1},\ldots,\cclrd{r_n},\cclrd{s_1},\ldots,\cclrd{s_m}}$.

@@

\subsection{Implicit parameters} In Haskell, implicit parameters \cite{app-implicit-parameters} are 
a special kind of variables that may behave as dynamically scoped. This means, if a function uses 
parameter $\ident{?p}$, then the caller of the function must define $\ident{?p}$ and set its value.
Implicit parameters can be used to parameterise a computation (involving a chain of function calls)
without passing parameters explicitly as additional arguments of all involved functions. A simple 
language with implicit parameters has an expression $\ident{?p}$ to read a parameter value and an 
expression\footnote{Haskell uses $\kvd{let}~\ident{?p} = e_1~\kvd{in}~e_2$, but we use a different keyword to 
avoid confusion.} $\kvd{letdyn}~?p = e_1~\kvd{in}~e_2$ that sets a parameter $\ident{?p}$ to the value of $e_1$ 
and evaluates $e_2$ in a context containing $\ident{?p}$

@@

\subsection{Type classes}
Implicit parameters are closely related to \emph{type classes} \cite{app-type-classes}. In Haskell,
type classes provide a principled form of ad-hoc polymorphism (overloading). When a code uses 
an overloaded operation (e.g.~comparison or numeric operators) a constraint is placed on the 
context in which the operation is used. For example:
%
\begin{equation*}
\begin{array}{l}
\ident{twoTimes}~::~\ident{Num}~\alpha \Rightarrow \alpha \rightarrow \alpha \\
\ident{twoTimes}~x=x+x
\end{array}
\end{equation*}
%
The constraint $\ident{Num}~a$ on the function type arises from the use of the $+$ operator. 
From the implementation perspective, the type class constraint means that the function takes 
a hidden parameter -- a dictionary that provides the operation $+ :: \alpha \rightarrow \alpha \rightarrow \alpha$.
Thus, the type $\ident{Num}~\alpha \Rightarrow \alpha \rightarrow \alpha$ can be viewed as
$(\ident{Num}_\alpha \times \alpha) \rightarrow \alpha$. Implicit parameters work in exactly
the same way -- they are passed around as hidden parameters.

@@

\subsection{Rebindable resources}
\label{sec:applications-flat-distr}

The need for parameters that do not strictly follow static scoping rules also arises in distributed
computing. This problem has been addressed, for example, by Bierman et al. and Sewell et al. 
\cite{app-distributed-rebinding,app-distributed-acute}. To quote the first work: \emph{``Dynamic 
binding is required in various guises, for example when a marshalled value is received from the 
network, containing identifiers that must be rebound to local resources.''}
